\chapter*{ABSTRACT}

The modern dynamics of housing and shared living arrangements have evolved
significantly, paving the way for innovative solutions to streamline the process
of finding roommates and renting accommodations. This project introduces a
comprehensive room renting application that revolutionizes the traditional
approach to housing searches by integrating collaborative features and
personalized matchmaking.\par

\vspace{0.3cm}
The core feature of this application is its versatility, offering users the
flexibility to either form teams to explore rental options collectively or
seek individual accommodations. The unique selling proposition (USP) lies
in its capability to facilitate seamless roommate searches for those seeking
cohabitation or simply looking to fill vacancies in existing spaces.\par

\vspace{0.3cm}

Key functionalities include a sophisticated matchmaking system leveraging user
preferences and profiles to pair compatible roommates and predicting accurate
renting price suggestions based on neighbourhood and amenities provided.
The application utilizes Next.js for its frontend, harnessing its capabilities
for dynamic and responsive web interfaces. Meanwhile, Supabase, a robust
PostgreSQL-based backend, powers the application's database, ensuring efficient
data management and scalability.

\vspace{0.3cm}

Through a user-centric design approach and a user-friendly interface, this
application aims to redefine the room renting experience, fostering connections,
and simplifying the often daunting task of finding suitable accommodations or
roommates.

\cleardoublepage
