\thispagestyle{empty}

\setcounter{page}{3}

\chapter*{Declaration of Authorship}

\vspace{1cm}

\noindent
We, \textbf{Ayush Kumar (LIT2020024) and Akshay Bhatnagar{LIT2020016}}, declare that the work presented in ``\textbf{HumaraGhar}" is our own. We confirm that:

\medskip

\begin{itemize}
      \item This work was completed entirely while in candidature for B.Tech. degree at Indian Institute of Information Technology, Lucknow.

            \medskip

      \item Where we have consulted the published work of others, it is always cited.

            \medskip

      \item Wherever we have cited the work of others, the source is always indicated. Except for the aforementioned quotations, this work is solely our work.

            \medskip

      \item We have acknowledged all major sources of information.
\end{itemize}

\vspace{2cm}

\noindent Signed:\\

\hspace{1.5cm}(Ayush Kumar) \hfill (Akshay Bhatnagar)
\rule[0.5em]{33em}{0.5pt}

\noindent Date:\\
\rule[0.5em]{33em}{0.5pt}

\cleardoublepage

\chapter*{CERTIFICATE}

This is to certify that the work entitled ``\textbf{HumaraGhar}" submitted by \textbf{Ayush Kumar and Akshay Bhatnagar} who got their name registered on \textbf{\;\;\; Jul 2020} for the award of B.Tech. degree at Indian Institute of Information Technology, Lucknow is absolutely based upon their own work under the supervision of \textbf{Dr. Mainak Adhikari}, Department of Computer Science, Indian Institute of Information Technology, Lucknow - 226 002, U.P., India and that neither this work nor any part of it has been submitted for any degree/diploma or any other academic award anywhere before.

\vspace{4cm}

\begin{center}
      Dr. Mainak Adhikari

      Department of Computer Science

      Indian Institute of Information Technology, Lucknow

      Pin - 226002, INDIA
\end{center}
