% Chapter 5

\chapter{Conclusion and Future Work} % Main chapter title

\label{Chapter5} % For referencing  use \ref{Chapter5} 

This semester-long project has culminated in the development of a comprehensive room renting application that caters not only to young professionals seeking shared accommodations but also to families and individuals in pursuit of independent renting options. Originating from our own experiences as young graduates navigating new cities, the application's inception aimed to address the challenges faced by various demographic segments in securing suitable accommodations.\par\medskip

The application's unique proposition lies in its versatility, allowing users to form teams for collaborative housing searches, find compatible roommates, or pursue independent renting without sharing. Leveraging sophisticated machine learning models, the platform aids in suggesting optimal rent prices for listed properties, empowering users with informed decisions.\par\medskip

Throughout the developmental phase, a user-centric approach guided the application's design and functionality. By harnessing Next.js for the frontend and Supabase for the backend, the platform ensures a dynamic, scalable, and intuitive experience for a diverse user base.\par\medskip

This project marks a significant step forward in providing solutions beyond the initial challenges faced by bachelor students entering new cities. The application serves as a comprehensive housing solution, addressing the needs of young professionals, families, and individuals seeking varied housing arrangements.\medskip
\clearpage

Looking ahead, several areas offer opportunities for further development and expansion:
\begin{enumerate}
    \item \textbf{Refinement of Machine Learning Algorithms:} Continuously improve the machine learning models to enhance the accuracy of rent price suggestions and roommate matchmaking, catering to the diverse needs of families and individuals.

    \item \textbf{Geographical and Demographic Expansion:} Expand the application's reach to encompass a broader range of cities and regions, considering the specific requirements of families and individuals seeking independent renting options.

    \item \textbf{Diversified User Experience:} Tailor the user experience to accommodate the distinct preferences of families and individuals, incorporating features like property size specifications, neighborhood suitability, and family-oriented amenities.

    \item \textbf{Accessibility and Inclusivity:} Ensure the application's accessibility for diverse user demographics by optimizing usability for individuals with varying needs and preferences.

    \item \textbf{Feedback-Driven Enhancements:} Implement a robust feedback mechanism to gather insights from families and individuals, enabling iterative improvements and customization based on their experiences and requirements.
\end{enumerate}
\bigskip
In conclusion, this project marks a significant achievement in providing a comprehensive room renting application that caters to the diverse housing needs of families, individuals seeking independent renting, and young professionals. As we move forward, the focus remains on continuous improvement and expansion, driven by user feedback and evolving housing trends.

