% Chapter 1

\chapter{Introduction}

\label{Chapter1}

\section{Background and Context}
In the evolving landscape of urban living, the challenges associated with
securing suitable accommodations transcend the boundaries of traditional
housing searches. Our endeavor to develop a room renting application stems
from the personal experiences of our team members—recent bachelor graduates
navigating their entry into professional realms in new, bustling cities.
The initial hurdle of securing affordable living spaces without an established
network of friends or acquaintances drove us to conceive a solution that
redefines the norms of housing searches.\par

\medskip

As young professionals transitioning from academic settings to bustling urban
environments, the lack of a supportive network to share the costs and experiences
of renting became a significant obstacle. This personal experience serves as the
driving force behind our initiative, inspiring us to craft a comprehensive
solution that addresses not only the financial burden but also the social and
logistical challenges associated with finding suitable accommodations and
compatible roommates.

\bigskip
``The Decision Diffie–Hellman assumption (DDH) is a gold mine," Dan Boneh wrote in his 1998
overview paper~\cite{boneh2006decision}.

\section{Need}
The contemporary housing market poses challenges for individuals transitioning
from academia to professional spheres, particularly in unfamiliar urban
landscapes. There exists a pressing need for an inclusive, efficient, and
user-centric platform that accommodates both solo renters and those seeking
collaborative living arrangements or compatible roommates. The absence of such
a tool creates inefficiencies and hurdles in finding affordable, compatible,
and convenient housing solutions.

\section{Problem Statement}
The challenge lies in bridging the gap between traditional housing approaches
and the modern needs of individuals seeking varied accommodation options.
The absence of a centralized platform that caters to both the individual
renter and those interested in collaborative living leads to prolonged
searches, incompatible living situations, and financial strains.

\section{Objectives}
\begin{enumerate}
    \item \textbf{Comprehensive Housing Searches:} Develop a platform that accommodates
          both individuals seeking independent rentals and those forming teams for
          collective exploration of rental spaces, ensuring inclusivity and
          convenience.
    \item \textbf{Efficient Roommate Matchmaking:} Create a robust matchmaking system
          that caters not only to those in search of compatible roommates but also to
          individuals seeking solo accommodations, ensuring tailored matches.
    \item \textbf{AI-Driven Rent Price Suggestions:} Utilize machine learning models t
          rained on diverse rent data to suggest optimal rent prices for listed
          properties, empowering users with informed pricing strategies.
    \item \textbf{Owner Dashboard \& Property Management:} Enable property owners to manage their
          listings through a dedicated dashboard, facilitating tasks like sending rent
          reminders, generating contract templates for rent agreements, and ensuring seamless
          property management.
    \item \textbf{Controlled Chat Feature:} Implement a secure and controlled chat function, allowing
          users to interact and negotiate further deals only with authorized and interested
          parties, enhancing user security and convenience.
    \item \textbf{User-Centric Design:} Prioritize user experience by delivering an intuitive
          interface that simplifies the search for accommodations or roommates,
          irrespective of the individual's preferences.
    \item \textbf{Addressing Financial and Social Barriers:} Alleviate the challenges associated
          with securing affordable living arrangements and establishing connections in
          new cities, catering to diverse housing needs.
\end{enumerate}

\section{Scope}
The project aims to develop a Next.js-based web application utilizing Supabase, a PostgreSQL-based
backend, to create a scalable, dynamic, and responsive platform. The focus lies in providing a
holistic solution catering to both individuals seeking independent rentals and those in search
of compatible roommates, fostering a sense of community and ease in the process of finding suitable
accommodations.Leveraging machine learning models, the platform will suggest rent prices for listed
properties, while a controlled chat feature will enable secure interactions between authorized users,
further enhancing the platform's utility and user experience.
